\begin{longtable}{| p{0.18\textwidth} | p{0.18\textwidth} | p{0.18\textwidth}*{12}{|p{0.01\textwidth} }| }
    \hline
    \textbf{OBJECTIVES} & \textbf{TARGET ACTIVITIES} & \textbf{TARGET ACCOMPLISHMENTS} (quantify, if possible) & \multicolumn{12}{|c|}{\textbf{YEAR 1}} \\
    \hline
     & & & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
    \hline
    Objective 1 & 
        To analyze constraints and requirements involved in UCTP, such as room availability, course prerequisites, and faculty courses. & 
    1. Gather data on room availability, course prerequisites, and faculty loads.\newline 
    2. Identify and categorize hard and soft constraints in UCTP.
        \off[8] \on[4] \\ 
    \hline
    Objective 2 & 
        To design and implement a Multi-Swarm Particle Swarm Optimization (MSPSO) algorithm to explore the solution space for course scheduling. & 
    1. Develop the MSPSO algorithm for course scheduling.\newline 
    2. Test and refine the algorithm using synthetic data.
        \off[8] \on[4] \\ 
    \hline
    Objective 3 & 
        To formulate an Integer Programming (IP) model specifically to enhance MSPSO-evolved solutions to fit hard constraints and maximize resource utilization. & 
    1. Develop the IP model to optimize resource utilization.\newline 
    2. Combine IP with MSPSO to improve solution accuracy and feasibility.
     \off[8] \on[4]  \\ 
    \hline
    \end{longtable}
    
    \begin{longtable}{| p{0.18\textwidth} | p{0.18\textwidth} | p{0.18\textwidth}*{12}{|p{0.01\textwidth} }| }
    \hline
    \textbf{OBJECTIVES} & \textbf{TARGET ACTIVITIES} & \textbf{TARGET ACCOMPLISHMENTS} (quantify, if possible) & \multicolumn{12}{|c|}{\textbf{YEAR 2}} \\
    \hline
     & & & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
    \hline
    
    Objective 4 & 
        To validate the hybrid MSPSO-IP model using real-time data. & 
    1. Collect real-time data for validation.\newline 
    2. Test the hybrid model in real-time scheduling scenarios.
        \on[5] \off[7] \\ 
    \hline
    Objective 5 & 
        To compare the hybrid model and existing algorithms in terms of performance. & 
    1. Compare performance metrics with existing algorithms such as PSO, GA.\newline 
    2. Conduct detailed benchmarking and performance analysis.
        \on[5] \off[7] \\ 
    \hline
    \end{longtable}
    