\section{Schedule of Activities}
\label{sec:schedule}

\begin{longtable}{| p{0.18\textwidth} | p{0.18\textwidth} | p{0.18\textwidth} *{12}{|p{0.02\textwidth} }| }
    \hline
    \textbf{OBJECTIVES} & \textbf{TARGET ACTIVITIES} & \textbf{TARGET ACCOMPLISHMENTS (Quantify, if possible)} & \multicolumn{12}{|c|}{\textbf{YEAR 1}} \\
    \hline
     & & & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
    \hline
    Solve UCTP via MSPSO & 
    Research and understand the UCTP domain and requirements. &
    Develop an initial solution model using MSPSO, test, and validate results. &
    & & & & & & & & \cellcolor{black!30} & \cellcolor{black!30} & \cellcolor{black!30} & \cellcolor{black!30} \\ 
    \hline
    Model UCTP in MSPSO &
    Integrate MSPSO framework with UCTP constraints and test parameters. &
    Create a working UCTP model aligned with real-world constraints. &
    & & & & & & & & & \cellcolor{black!30} & \cellcolor{black!30} & \cellcolor{black!30} \\ 
    \hline
    Compare MSPSO vs others &
    Conduct comparative analysis with other swarm approaches, etc. &
    Publish comparative performance results with analysis. &
    & & & & & & & & & & & \cellcolor{black!30}\\ 
    \hline
    Deploy MSPSO app &
    Deploy an interactive MSPSO web app using Streamlit. &
    Functional deployment of MSPSO for end-user testing and evaluation. &
    & & & & & & & & & & &\\ 
    \hline
\end{longtable}

\begin{longtable}{| p{0.18\textwidth} | p{0.18\textwidth} | p{0.18\textwidth} *{12}{|p{0.02\textwidth} }| }
    \hline
    \textbf{OBJECTIVES} & \textbf{TARGET ACTIVITIES} & \textbf{TARGET ACCOMPLISHMENTS (Quantify, if possible)} & \multicolumn{12}{|c|}{\textbf{YEAR 2}} \\
    \hline
     & & & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
    \hline
    Compare MSPSO vs others &
    Detailed benchmarking of MSPSO against alternatives, further refinements. &
    Publish final results and improvements for UCTP. &
    \cellcolor{black!30} & \cellcolor{black!30} & \cellcolor{black!30} & \cellcolor{black!30} & \cellcolor{black!30} & \cellcolor{black!30} & & & & & & \\ 
    \hline
    Deploy MSPSO app &
    Deploy refined MSPSO-based application for wider usability. &
    Final app deployment with extended features. &
    & & & & \cellcolor{black!30} & \cellcolor{black!30} & & & & & & \\ 
    \hline
\end{longtable}
\break